---
title: "SPY vs SPXS Impact on other tickers"
output:
  html_document:
    df_print: paged
---

The purpose of this code is to find best buying oppurtunity using SPY and SPXS as indicators.

```{r, echo = FALSE, warning=FALSE, message=FALSE}
library(quantstrat)
```

###Functions
All the functions created for this project will be stored under this.

```{r functions}
adjustStartDate <- function(syms.company, syms.Index) {
  data.company <- get(syms.company)
  firstDate <- first(index(data.company))
  lastDate <- last(index(data.company))
  index.short <- paste(firstDate, lastDate, sep = "/")
  
  for (i in 1: length(syms.Index)) {
    data.Index.temp <- get(syms.Index[i])
    data.Index.temp <- data.Index.temp[index.short]
    assign(syms.Index[i], data.Index.temp, envir = .GlobalEnv)
  }
  print("All data have same starting and ending date")
}
```
###Select symbols
We have divided symbols into two categories. Indicators (index) and company or ticker
Since some company's data is shorter than indicators, the ```adjustStartDate()``` function 
will make them all equal size in order to avoid error.

```{r load data, message=FALSE}
syms.Index <-c("SPY", "SPXS")
syms.company <- "CLDR"
getSymbols(syms.Index)
getSymbols(syms.company)
adjustStartDate(syms.company, syms.Index)
```

